Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-26 ms.tex
added an explanation of how the spectral tracers were found.
I added some quick spectrum of an initial reduction of one KIC 1255 file.

We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.

>>>>

We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

The 2013 HDS data for KIC 1255 display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D line.
There are many bad pixels.}\label{fig:naDline}
\end{centering}
\end{figure}
